Oral Manuscript

### 2018-06-20 03-Details.Rmd
test

\begin{align*}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{align*}

@@

<br><br>\newpage

<!-- \begin{thebibliography}{9} -->

<!-- \bibitem{1} -->
<!--   Boyd, Stephen, et al. "Distributed optimization and statistical learning via the alternating direction method of multipliers." Foundations and Trends® in Machine Learning 3.1 (2011): 1-122. -->

<!-- \bibitem{2} -->
<!--   Polson, Nicholas G., James G. Scott, and Brandon T. Willard. "Proximal algorithms in statistics and machine learning." Statistical Science 30.4 (2015): 559-581. -->

<!-- \bibitem{3} -->
<!--   Marjanovic, Goran, and Victor Solo. "On $ l_q $ optimization and matrix completion." IEEE Transactions on signal processing 60.11 (2012): 5714-5724. -->

<!-- \bibitem{4} -->
<!--   Zou, Hui, and Trevor Hastie. "Regularization and variable selection via the elastic net." Journal of the Royal Statistical Society: Series B (Statistical Methodology) 67.2 (2005): 301-320. -->

<!-- \end{thebibliography} -->

## References

>>>>

$$ \begin{align*}
  \mbox{minimize } f(x) + g(z) \\
  \mbox{subject to } Ax + Bz = c
\end{align*} $$

@@
